---
title: "Report#1"
author: "Parimah Emadi"
date: "9/10/2022"
output:
  pdf_document: default
  html_document: default
---
##Loading packages
 
     

```{r}
library(limma)
library(pheatmap)
library(ggplot2)
library(reshape2)
library(plyr)
library(data.table)
library(ggpubr)
theme_set(theme_pubr())
```

##Loading Expression Matrices 


```{r}
setwd("/Users/sayeh/Documents/uni/pRact/ThesisCode/data/NormalizedDataRMA/")

Data1 <- read.delim("GSE6575NormalMatrix.txt", sep = " ")  #GPL570
Data2 <- read.delim("GSE89594NormalMatrix.txt", sep = " ") #GPL16699** , one color, GeneSymbol in End
Data3 <- read.delim("GSE26415NormalMatrix.txt", sep = " ")  #GPL6480 , one color, GeneSymbol in End
Data4 <- read.delim("GSE18123NormalMatrix.txt", sep = " ") #GPL6244

```

The expression distribution of all datasets were `r summary(Data1)`, `r summary(Data2)`, `r summary(Data3)` , `r summary(Data4)` with the boxplot: 

```{r}

par(mfrow=c(2,2))
boxplotDatas <- lapply(Datas, boxplot)

```

Data 1 & 4 both are affymetrix with same summary report of quantiles as for 2,3 agilent arrays

Assigning "GeneSymbol" as a shared colomn in all datasets
```{r}
colnames(Data1)[2] <- "GeneSymbol"
colnames(Data2)[95] <- "GeneSymbol"
colnames(Data3)[85] <- "GeneSymbol"
colnames(Data4)[2] <- "GeneSymbol"

```

Removing ID cols and gene symbols with more than one names "///" 

```{r}
Data1$`GeneSymbol` <- sub("/.*", "", Data1$`GeneSymbol`)
Data4$`GeneSymbol` <- sub("/.*", "", Data4$`GeneSymbol`)
Data1 <- Data1[,-1]
Data4 <- Data4[,-1]

```



```{r}

```



```{r}

```



